---
title: "Nutrients_2017"
author: "Lauran Liggan"
date: "10/23/2018"
output: html_document
---

### --- Hakai Surface Water Grabs (Nutrients) data loading and formatting ---

#### This script contains code for loading and [some simple] tidying of the
#### Hakai Surface Water Grabs data subsets, specificallty PO4, Si, and Nitrates as well as any necessary packages. 


#### The following script will load the above dataset, as well as do some minor
####  formatting (ie. set variable classes, create new variables, rename
####   variables, etc.).


### --- Packages ---
####   The following code installs and loads all the necessary packages. It is commented out by default.Be sure to check you have all these packages
####   installed, remove the comment and run if necessary, otherwise the majority of summaries and figures will not work.

#### Install packages ---

```{r packages}

lapply(c("dplyr", "ggplot2", "magrittr", "reshape2", "lubridate"),
       library, character.only = T)

library(plotly)
library(googlesheets)
library(ggthemes)
library(ggplot2)
library (Rmisc)
library(cowplot)
library(gridExtra)
```
### --- Packages end ----

### --- Load data ---
####   The following code loads the DO13C datasets, rename some variables,
####   and create some new variables.

#### Set a loading directory ---
#### Save all csv files in Nutrients -> 2017 -> Data folder on Dropbox

```{r directory}
setwd("~/Dropbox/Projects/Hakai Projects/Surface Water Grabs/Nutrients/2017/Data") 

getwd()

```

#### Load Nutrient data ---
#### Data has been manually cleaned


```{r load}
LL2017_nutrientsData <- read.csv(file="~/Dropbox/Projects/Hakai Projects/Surface Water Grabs/Nutrients/2017/Data/Nutrients_ROCKY_cleaned_LL.csv",
                                 header           = TRUE,
                                 stringsAsFactors = FALSE) %>%
  
  mutate(Site             = as.factor(ifelse(Site == "ROCKY02", "Foggy Cove",
                                      ifelse(Site == "ROCKY04", "Little Wolf", 
                                      ifelse(Site == "ROCKY05", "Nalau",
                                      ifelse(Site == "ROCKY03", "5th Beach",
                                      ifelse(Site == "ROCKY06", "West Beach",
                                      ifelse(Site == "ROCKY07", "North Beach",NA))))))))

glimpse(LL2017_nutrientsData)
```

### --- Load data end ---

### --- Clean data ---

#### Clean Nutrient dataset ---

```{r clean}
Nutrients2017 <- na.omit(LL2017_nutrientsData)
NROW(Nutrients2017)

Nutrients2017$month <- factor(Nutrients2017$month)

Nutrients2017$month <- factor(Nutrients2017$month, levels = c("April","May", "June", "July", "August"))
```

### --- Clean data end ---


### --- Summary figures ---
#### Nutrient summary figures --- 

```{r aesthetics}
# format aesthetics
theme_set(theme_classic(base_size = 16))

pd <- 0.5

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

#### PO4

```{r nutsPO4Fig, echo=FALSE, fig.height=5, fig.width=13}
nutsPO4Fig <- ggplot(Nutrients2017, aes(x= month, y= PO4, col=Site)) +
  geom_point( position=position_dodge(pd), size =3) +
  geom_line( position=position_dodge(pd), aes(group=Site), linetype= 2) +
  theme(panel.grid.major = element_line(colour = "grey90", linetype = 3)) +
  scale_color_manual(values = cbPalette) + 
  ylab("PO4") +
  xlab("Month") +
  facet_wrap(~Site, ncol = 6) +
  theme(axis.text.x=element_text(hjust=1)) +
  ggtitle(~italic("Nearshore Surface Water (2017)"), "Nutrients") + 
  theme(plot.title = element_text(hjust = -0.01, vjust=1.12, size =20)) +
  theme(legend.position="none")+
  theme(axis.title.x=element_blank(),axis.text.x=element_blank())  

nutsPO4Fig

```

### print figure
```{r nutsPO4Fig_print, echo=FALSE}
nutsPO4Fig_print <- ggsave(plot = nutsPO4Fig, width = 5, height = 13, dpi = 600, filename = "Nuts_PO4_2017.tiff")
```

#### Si 

```{r nutsSiFig, echo=FALSE, fig.height=5, fig.width=13}
nutsSiFig <- ggplot(Nutrients2017, aes(x= month, y= SiO2, col=Site)) +
  geom_point( position=position_dodge(pd), size=3) +
  geom_line( position=position_dodge(pd), aes(group=Site), linetype= 2) +
  theme(panel.grid.major = element_line(colour = "grey90", linetype = 3)) +
  scale_color_manual(values = cbPalette) + 
  ylab("SiO2") +
  xlab("Month") +
  scale_y_continuous(breaks = seq(0, 15, len = 6)) +
  facet_wrap(~Site, ncol = 6) +
  theme(strip.background = element_blank(), strip.text.x = element_text(size=0)) +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank()) +
  theme(legend.position="none")

nutsSiFig

```

### print figure
```{r nutsSiFig_print, echo=FALSE}
nutsSiFig_print <- ggsave(plot = nutsSiFig, width = 5, height = 13, dpi = 600, filename = "Nuts_Si_2017.tiff")
```

#### Nitrates

```{r nutsNitFig, echo=FALSE, fig.height=5, fig.width=13}
nutsNitFig <- ggplot(Nutrients2017, aes(x= month, y= NO3.NO2, col=Site)) +
  geom_point( position=position_dodge(pd), size=3) +
  geom_line( position=position_dodge(pd), aes(group=Site), linetype= 2) +
  theme(panel.grid.major = element_line(colour = "grey90", linetype = 3)) +
  scale_color_manual(values = cbPalette) + 
  ylab("NO3 + NO2") +
  xlab("Month") +
  facet_wrap(~Site, ncol = 6) +
  scale_y_continuous(breaks = seq(0, 8, len = 5)) +
  theme(strip.background = element_blank(), strip.text.x = element_text(size=0)) +
  theme(axis.text.x=element_text(hjust=1)) +
  theme(legend.position="none")+
  theme(axis.text.x=element_text(hjust=1, angle=45))  

nutsNitFig

```

### print figure
```{r nutsNitFig_print, echo=FALSE}
nutsNitFig_print <- ggsave(plot = nutsNitFig, width = 5, height = 5, dpi = 600, filename = "Nuts_Nitrate_2017.tiff")
```

#### Combined figure

```{r g, echo=FALSE, fig.height=10, fig.width=10}
# stack all graphs into one figure

library(grid)
gl = lapply(list(nutsPO4Fig, nutsSiFig,nutsNitFig), ggplotGrob) 
library(gtable)
g = do.call(rbind, c(gl, size="first"))
g$widths = do.call(unit.pmax, lapply(gl, "[[", "widths"))
grid.newpage()
grid.draw(g) 

```

### print figure
```{r g_print, echo=FALSE}
g_print <- ggsave(plot = g, width = 10, height = 10, dpi = 600, filename = "Nutrients_2017.tiff")
```

#### --- Nutrient summary figures end ---
